
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Visinigiri Jayant} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} {9508309972}
    $|$
    \faAt \hspace{.5pt} \href{mailto:visinigirijayant@gmail.com}{visinigirijayant@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/visinigiri-jayant/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/Jayantrao001}{Github}
    $|$
    
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeSubheading
{Vellore Institute of Technology (VIT)
}{Vellore}
{B.Tech.  in Electronics & Communication Engineering;   \textbf{CGPA: 8.55}}{Sept. 2021 \textbf{--} Jul. 2025}

\resumeSubheading
{Kerala Samajam Model School
}{Jamshedpur}
{ISC in PCM;   \textbf{CGPA: 77.25\%}}{Mar. 2020 \textbf{--} Jul. 2021}


  \resumeSubHeadingListEnd


%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeSubheading
      {KPIT Technologies Ltd.}{Pune}
      {Associate Engineer}{Jan. 2025 \textbf{--} Present}
      \resumeItemListStart
      \resumeItem{Develop embedded software components for automotive ECUs (Electronic Control Units).}\resumeItem{Work on technologies like AUTOSAR, Model-Based Development (MBD), and diagnostics (UDS, CAN).}\resumeItem{Perform software testing (unit, integration, and validation).}
        \resumeItemListEnd

\resumeSubheading
      {Tata Steel}{Jamshedpur}
      {Trainee}{Aug. 2023 \textbf{--} Sept. 2023}
      \resumeItemListStart
      \resumeItem{Conducted maintenance and troubleshooting of electrical and electronic systems.}\resumeItem{Diagnosed and repaired equipment issues to improve operational efficiency by 15\%.}\resumeItem{Gained hands-on experience in fieldwork and technical problem-solving in a manufacturing environment.}
        \resumeItemListEnd


  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeProjectHeading
{\textbf{IoT-Based Smart Fire Safety System | Simulation Project | Cisco Packet Tracer} $|$ \underline{\emph{\href{https://github.com/Jayantrao001/fire_safety_system}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Simulated an IoT-based fire safety system using Cisco Packet Tracer with integrated smoke detectors, sprinklers, sirens, and smart devices.}\resumeItem{Emphasized real-time monitoring and automated emergency response to improve residential fire safety.}\resumeItem{Optimized sensor placement and system configuration for enhanced responsiveness and efficiency.}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{Smart Plant Monitoring System | Smart Agriculture | ESP8266 NodeMCU} $|$ \underline{\emph{\href{https://github.com/Jayantrao001/smart-plant-monitoring-system}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Designed an IoT-based smart plant monitoring system using ESP8266 NodeMCU and environmental sensors.}\resumeItem{Integrated temperature, humidity, and soil moisture sensors to enable real-time plant health tracking.}\resumeItem{Automated irrigation through a relay-controlled pump with mobile and web dashboard controls for remote access.}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{RISC-V Processor Component Design | Processor Architecture | Verilog HDL} $|$ \underline{\emph{\href{https://github.com/Jayantrao001/risc-v-component-design}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Contributed to the design and verification of RISC-V processor components using Verilog HDL.}\resumeItem{Focused on optimizing architecture-level functionality for efficient simulation and performance.}\resumeItem{Achieved a 20\% reduction in simulation time, enhancing overall system efficiency.}
        \resumeItemListEnd


  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeItemListStart
  \resumeItem{Identified as a Top Coder, VIT University $|$ \underline{\emph{\href{Ranked among the top 2\% in competitive coding out of 12,000+ participants at VIT University. This achievement reflects a high level of proficiency in JAVA and algorithmic problem-solving skills.}{Link}}}}\resumeItem{Conference Paper Publication $|$ \underline{\emph{\href{Published a paper on Smart Plant Monitoring and IoT-Based Fire Safety systems, showcasing real-time IoT automation using ESP8266 and Cisco Packet Tracer.}{Link}}}}
  \resumeItemListEnd


%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

  
    \textbf{Programming Languages:}{ Embedded C, JAVA, C/C++, SQL, Verilog, System Verilog} \ \vspace{3pt}

    \textbf{Hardware Design:}{ Digital Circuits, Microcontroller, HDL (Verilog, VHDL)} \ \vspace{3pt}

}}
\resumeSubHeadingListEnd



%----------- Profiles -----------

\section{Profiles}
  \vspace{2pt}
  \resumeItemListStart
  \resumeItem{\underline{\href{https://github.com/Jayantrao001/}{GitHub}}}
  \resumeItemListEnd

%-------------------------------------------
\end{document}
