
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Aryan} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} {6200544626}
    $|$
    \faAt \hspace{.5pt} \href{mailto:aryansinghrishu1001@gmail.com}{aryansinghrishu1001@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/aryan-22a75335b/}{LinkedIn}
    $|$
    
    $|$
    
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeSubheading
{Vellore Institute of Technology (VIT)
}{Vellore}
{B.Tech.  in Mechanical in Automotive;   \textbf{CGPA: 7.9}}{Sept. 2021 \textbf{--} Jul. 2025}

\resumeSubheading
{M.G.M.H.S. School
}{Bokaro}
{CBSE (CLASS XII) in PCM;   \textbf{CGPA: 79}}{Mar. 2020 \textbf{--} April 2021}

\resumeSubheading
{M.G.M.H.S. School
}{Bokaro}
{CBSE (CLASS X) in ;   \textbf{CGPA: 86}}{Mar. 2018 \textbf{--} April 2019}


  \resumeSubHeadingListEnd


%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeSubheading
      {SAIL}{Bokaro Steel City, Jharkhand}
      {Trainee}{Aug. 2023 \textbf{--} Sept. 2023}
      \resumeItemListStart
      \resumeItem{Completed 28-day vocational training at SAIL Bokaro’s Cold Rolling Mill (CRM 1 & 2), gaining exposure to steel processing operations like pickling, tandem rolling, annealing, and galvanizing.}\resumeItem{Studied and analyzed industrial hydraulic circuits, including components such as pumps, valves, and cylinders, and their applications in steel manufacturing.}\resumeItem{Collaborated with plant engineers and managers, adhering to industrial safety protocols while observing real-time mechanical operations and system workflows.}
        \resumeItemListEnd


  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeProjectHeading
{\textbf{Experimental Analysis of Floating Solar PV Panel Using Thermal Storage} $|$ \underline{\emph{\href{}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Designed and developed a floating solar PV panel system integrated with Phase Change Material (PCM) to reduce panel surface temperature by 6–10°C and enhance efficiency.}\resumeItem{Conducted experimental testing to compare temperature, voltage, and output power across different tilt angles (30°, 35°, 40°), demonstrating 5–6\% performance gain using thermal storage.}\resumeItem{Modeled the floating structure using SolidWorks and built the prototype using marine-grade plywood for buoyancy, validating it under varying environmental conditions.}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{Emission Testing Through Various Biodiesel Using Waste Vegetable Oil} $|$ \underline{\emph{\href{}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Designed and conducted experiments to produce biodiesel from waste vegetable oil using transesterification, and tested blends (B20, B50, B100) for engine performance and emission levels.}\resumeItem{Analyzed emission data (CO, NOx, PM, SO₂) using SCR and EGR technologies, achieving up to 35\% reduction in CO and PM and exploring near-zero NOx feasibility.}\resumeItem{Validated fuel properties and quality through lab testing and developed optimization strategies for catalyst ratios, blending conditions, and emission control techniques.}
        \resumeItemListEnd


  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeItemListStart
  \resumeItem{Advance Diploma in Computer Application (ADCA) }
  \resumeItemListEnd


%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

  
    \textbf{Design & Engineering Tools:}{  AutoCAD, SolidWorks, MATLAB, MS Office} \ \vspace{3pt}

    \textbf{Soft Skills:}{ Conflict Resolution, Leadership, Critical Thinking, Adaptability} \ \vspace{3pt}

}}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
